---
title: "demo"
output: pdf_document
---

## In R

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This file demonstrates how to use the stattotex package.

First, we install and set up the package from GitHub.

```{r setup, message=FALSE}
library(devtools)
devtools::install_github("ijyliu/stattotex-R")
library(stattotex)
```

Suppose we had some calculated statistic/variable. For example, we could compute average monthly sales for a product over the previous quarter. Suppose that this statistic takes on the value of 2,532.01 units.

```{r}
number <- 2532.01
```

Let us now save this number to the file "demoNums.tex" with the name "AvgMonthlySales". We can use the setting clear_file=TRUE to delete the file before writing to it.

```{r}
stattotex(variable_name="AvgMonthlySales", 
          variable_value=number, 
          filename="demoNums.tex", 
          clear_file=TRUE)
```

Let's say we wish to format this as 2,532.01. We can directly format the number as a string, and feed strings to stattotex.

```{r}
f_number <- formatC(number, format = "f", digits = 2, big.mark = ",")
```

This function call will update the value of the number for LaTeX.

```{r}
stattotex("AvgMonthlySales", f_number, "demoNums.tex")
```

stattotex will accept arbitrary string inputs. Let's say our sales increased by 100.3% from the previous quarter

```{r}
pct <- 100.3
pct_string <- paste0(as.character(pct), "%")
stattotex("SaleIncPct", pct_string, "demoNums.tex")
```

and we want to say that the sales increased/decreased/stayed the same based on the percentage

```{r}
if (pct > 0.0) {
  word <- "increased"
} else if (pct == 0.0) {
  word <- "stayed the same"
} else {
  word <- "decreased"
}
stattotex("SaleDir", word, "demoNums.tex")
```

## In LaTeX

We can now compile a document making use of these numbers. Check out the `Demo Report.tex` file in this folder, and the associated `Demo Report.pdf` created.

```{r, message=FALSE, warning=FALSE, error=FALSE}
install.packages('tinytex', repos = "https://cloud.r-project.org")
if (!tinytex::is_tinytex()) {
  tinytex::install_tinytex() 
}
tinytex::pdflatex('Demo Report.tex')
```
